Prospective testing for the prevalence or transience of a shock effect before it occurs

### 2021-11-03 prevalence_testing/postshocktest2021draft.tex
minor edits

  \tilde{\mathbf{\theta}}_{i,j} &= \theta_{i,j} + \gamma_{i,j}, j = 1,\ldots, q_{2}, \; \text{where} \; \gamma_{i,j} \simiid \mathcal{F}_{\gamma} \; \text{with} \; \mrm{E}_{\mathcal{F}_{\gamma}}(\gamma_{i,j}) = \beta_o + \beta\mbf{x}_{i,T_i^*+1}, \mrm{Var}_{\mathcal{F}_{\gamma}}(\gamma_{i,j}) = \Sigma^2_\gamma,  \\  

@@

\tilde{\mathbf{\phi}}_{i,j} \indep \lambda_{i,j} \indep \gamma_i \indep \mathbf{\delta}_i \indep \varepsilon_{i,t} \indep \tilde\varepsilon_{i}, 

@@

where the distribution $\mathcal{F}_{\tilde{\mathbf{\phi}}_j}(\x_{i,T_i^*+1})$ exists between -1 and 1 and $\mrm{E}(\mathcal{F}_{\tilde{\mathbf{\phi}}_j}(\x_{i,T_i^*+1})) - \mrm{E}(\mathcal{F}_{\tilde{\mathbf{\phi}}_j}(\x_{j,T_i^*+1})) \to 0$ as $\|\x_{i,T_i^*+1} - \x_{j,T_i^*+1}\| \to 0$.

@@

The model \eqref{model-gen} with the above random effects structure is a generalization of both model formulations in \cite{lin2021minimizing}. \textbf{Need to carefully show}. Note that for model \eqref{model-gen} to be of use for post-shock forecasting, the variation in $\mathcal{F}_{\tilde{\mathbf{\phi}}}$ needs to be small relative to the signal captured in $\x_{i,T_i^*}$, and $\sigma^2_\alpha$ and $\Sigma^2_\gamma$ needs to be small relative to $\mu_\alpha + \delta_i'\x_{i,T_i^*}$ and $\beta_o + \beta\mbf{x}_{i,T_i^*+1}$ respectively.

We see that model \eqref{model-gen} with its accompanying random effects structure is flexible enough to capture changing structural dynamics as well as a mean-shift. These dynamic changes depend heavily on the value of $\mbf{x}_{i,T_i^*+1}$. Two series $i,j$ with small $\|\mbf{x}_{i,T_i^*+1} - \mbf{x}_{j,T_i^*+1}\|_2$ are expected to experience similar structural changes. This makes distance based weighting an attractive avenue.

>>>>

  \tilde{\mathbf{\theta}}_{i,j} &\overset{ind}{\sim} \mathcal{F}_{\tilde{\mathbf{\theta}_j}}(\x_{i,T_i^*+1}),  \\  

@@

\tilde{\mathbf{\phi}}_{i,j} \indep \lambda_{i,j} \indep \mathbf{\delta}_i \indep \varepsilon_{i,t} \indep \tilde\varepsilon_{i}, 

@@

%where the distributions $\mathcal{F}_{\tilde{\mathbf{\phi}}_j}(\x_{i,T_i^*+1})$ and $\mathcal{F}_{\tilde{\mathbf{\theta}}_{i'}}(\x_{i,T_i^*+1})$ are such that $\mrm{E}(\mathcal{F}_{\tilde{\mathbf{\phi}}_i}(\x_{i,T_i^*+1})) - \mrm{E}(\mathcal{F}_{\tilde{\mathbf{\phi}}_j}(\x_{i',T_i^*+1})) \to 0$ as $\|\x_{i,T_i^*+1} - \x_{i',T_i^*+1}\| \to 0$.

@@

%The model \eqref{model-gen} with the above random effects structure is a generalization of both model formulations in \cite{lin2021minimizing}. \textbf{Need to carefully show}. Note that for model \eqref{model-gen} to be of use for post-shock forecasting, the variation in $\mathcal{F}_{\tilde{\mathbf{\phi}}}$ needs to be small relative to the signal captured in $\x_{i,T_i^*}$, and $\sigma^2_\alpha$ and $\Sigma^2_\gamma$ needs to be small relative to $\mu_\alpha + \delta_i'\x_{i,T_i^*}$ and $\beta_o + \beta\mbf{x}_{i,T_i^*+1}$ respectively. 
where the distributions $\mathcal{F}_{\tilde{\mathbf{\phi}}_j}(\x_{i,T_i^*+1})$ and $\mathcal{F}_{\tilde{\mathbf{\theta}}_{i'}}(\x_{i,T_i^*+1})$ satisfy $\mathcal{F}_{\tilde{\mathbf{\phi}}_j}(\x_{i,T_i^*+1}) \overset{d}{=} \mathcal{F}_{\tilde{\mathbf{\phi}}_{j}}(\x_{i',T_i^*+1})$ and $\mathcal{F}_{\tilde{\mathbf{\theta}}_j}(\x_{i,T_i^*+1}) \overset{d}{=} \mathcal{F}_{\tilde{\mathbf{\theta}}_{j}}(\x_{i',T_i^*+1})$ when $\x_{i,T_i^*+1} = \x_{i',T_i^*+1}$. Note that for model \eqref{model-gen} to be of use for post-shock forecasting, the variation in $\mathcal{F}_{\tilde{\mathbf{\phi}}}$ and $\mathcal{F}_{\tilde{\mathbf{\theta}}}$ must be small relative to the signal strength.

We see that model \eqref{model-gen} with its accompanying random effects structure is flexible enough to capture changing structural dynamics as well as a mean-shift. These dynamic changes depend heavily on the value of $\mbf{x}_{i,T_i^*+1}$, the covariates recorded right before the first post-shock response is observed. Under this setup any two series $i,j$ with small $\|\mbf{x}_{i,T_i^*+1} - \mbf{x}_{j,T_i^*+1}\|_2$ are expected to experience similar structural changes. This makes distance based weighting an attractive avenue.
